How Kids Code and How We Know:\\An Exploratory Study on the Scratch Repository

### 2016-06-14 Paper/paper.tex
Corrected mistake on percentage of decision points

\noindent
\fbox{
	\begin{minipage}{0.46\textwidth}
		RQ1: The majority of Scratch projects are small and simple; 75\% of the projects have up to 5 sprites, 12 scripts, 76 blocks and no decision points. Most code is written in sprites. There exist surprisingly large and complex projects.
	\end{minipage}}

>>>>

\noindent
\fbox{
	\begin{minipage}{0.46\textwidth}
		RQ1: The majority of Scratch projects are small and simple; 75\% of the projects have up to 5 sprites, 12 scripts and 76 blocks. The majority (78\%) of scripts contain no decision points. Most code is written in sprites. There exist surprisingly large and complex projects.
	\end{minipage}}
